Coherent optical association of a single molecule -- Supplemental material

### 2020-11-24 sm.tex
Update on Overleaf.

\section{Excited Molecular States} 
The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P. These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}. Potential energy curves for $\mathrm{c^3\Sigma^+_{\Omega = 1}}$ and $  B^1\Pi_{\Omega = 1} $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}. Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{b-A} complex.

>>>>

\section{Excited Molecular States} 
The lowest eight molecular potentials in NaCs asymptote to the dissociation limit of Na 3S + Cs 6P. These eight potentials can be written in the Hund's case (a) basis as $ \mathrm{c^3\Sigma^+_{\Omega = 0^-},c^3\Sigma^+_{\Omega = 1}, b^3\Pi_{\Omega = 0^-}, b^3\Pi_{\Omega = 0^+}, b^3\Pi_{\Omega = 1}, b^3\Pi_{\Omega = 2}, B^1\Pi_{\Omega = 1}, A^1\Sigma^+_{\Omega = 0^+}}$ \cite{Korek2007}. Potential energy curves for $\mathrm{c^3\Sigma^+_{\Omega = 1}}$ and $  B^1\Pi_{\Omega = 1} $ have been experimentally determined, and are predictive across the entire energy range of the potential \cite{Grochola2010, Grochola2011, Liu2017}. Due to the large spin-orbit coupling present in Cs, a deperturbation analysis was required for states belonging to the mixed \mathrm{A-b} complex \cite{Zaharova2009}. Since we are most closely detuned from the $  $
